\thetitle

### 2008-06-13 paper.tex
Lots of work on Common Assumptions section.

The \caps{GMM} has the benefit of making the conditioning of behaviors completely explicit. It also allows us to easily define intermediate choices. If we wish make the behavior of each flow a weighted average of the aggregate behaviors of its source and destination nodes, we can express this easily:
\begin{align}
\mat{F}' = ((1-\alpha)\,\rStoch(\trans{\mat{S}}\mat{S})+(\alpha)\,\rStoch(\trans{\mat{D}}\mat{D}))\mat{F}.
\end{align}
The parameter $\alpha$ allows us to smoothly vary the weighting of the source and destination behaviors. Source-only behavior is given by $\alpha=0$; destination-only by $\alpha=1$; to weight source and destination equally, take $\alpha=\frac{1}{2}$.

>>>>

The \caps{GMM} has the benefit of making the conditioning of behaviors completely explicit. It also allows us to easily define intermediate choices. If we wish make the behavior of each flow a weighted average of the composite behaviors of its source and destination nodes, we can express this easily:
\begin{align}
\mat{F}' = ((1-\alpha)\,\rStoch(\trans{\mat{S}}\mat{S})+(\alpha)\,\rStoch(\trans{\mat{D}}\mat{D}))\mat{F}.
\end{align}
The parameter $\alpha$ allows us to smoothly vary the weighting of the source and destination behaviors. Source-only behavior is given by $\alpha=0$; destination-only by $\alpha=1$; to weight source and destination equally, take $\alpha=\frac{1}{2}$.
